Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-15 article.tex

Even when a diversification model passes the procedure described above,
it is not necessarily used in Bayesian inference.
In Bayesian inference, the likelihood of a diversification 
model, is computed millions of times.
Due to this, effective but computationally expensive tree priors are non-viable.
Also, there may be no need to add such a tree prior to a Bayesian
inference framework: the more informative the data, 
the lower the influence the tree prior has.
Due to this, computationally faster tree priors are more commonly used.
However, it is unknown if it is valid to assume that tree prior choice is 
of low importance.

There have been multiple attempts to investigate the importance of tree
prior choice. For example, recently Sarver et al., [\cite{sarver2019choice}] 
show that the choice of tree prior does not 
substantially affect phylogenetic inferences of diversification rates.
Also recently, Duchene et al. [\cite{duchene2018phylodynamic}] released
a BEAST2 package to assess how well posterior predictive simulations
recover a given tree when using the standard diversification models.
These investigations show how current diversification models compare
to one another, but these do not help to assess the importance of a 
new tree prior.

>>>>

Even when a diversification model passes the procedure described above,
it is not necessarily used in Bayesian inference.
In these kind of procedures the likelihood of a diversification 
model can be computed millions of times.
Due to this, effective but computationally expensive tree priors are non-viable.
Also, there may be no need to add such a tree prior to a Bayesian
inference framework: the more informative the data, 
the lower the influence the tree prior has.
Due to this, computationally faster tree priors are more commonly used.
However, it is unknown if it is valid to assume that tree prior choice is 
of low importance.

There have been multiple attempts to investigate the importance of tree
prior choice. For example, recently Sarver et al., [\cite{sarver2019choice}] 
show that the choice of tree prior does not 
substantially affect phylogenetic inferences of diversification rates.
Also recently, Duchene et al. [\cite{duchene2018phylodynamic}] released
a BEAST2 package to assess how well posterior predictive simulations
recover a given tree when using the standard diversification models.
These investigations show how current diversification models compare
to one another, but they do not help to assess the importance of a 
new tree prior.
